Optimal (Multiway) Spatial Joins

### 2024-05-27 msj.tex
yufei

\extraspacing {\underline{\em Example.}} To illustrate our algorithm, we will utilize the running example in Figure~\ref{fig:hv:type1:ex}a, where $k = 4$, and $R_1 = \set{\alpha}$, $R_2 = \set{\beta_2, \beta_2}$, $H$ $=$ $\set{h_1,$ $h_2,$ $..., h_6}$, and $V = \set{v_1, v_2, ..., v_5}$. The set $\J_1$ contains the following 4-tuples: $(\alpha, \beta_2, h_2, v_3)$, $(\alpha, \beta_2, h_2, v_5)$, $(\alpha, \beta_2, h_5, v_3)$, and $(\alpha,$ $\beta_2, h_5, v_6)$. \qed

@@

@@

>>>>

\extraspacing {\underline{\em Example.}} To illustrate our algorithm, we will utilize the running example in Figure~\ref{fig:hv:type1:ex}a, where $k = 4$, and $R_1 = \set{\alpha}$, $R_2 = \set{\beta_2, \beta_2}$, $H$ $=$ $\set{h_1,$ $h_2,$ $..., h_6}$, and $V = \set{v_1, v_2, ..., v_5}$. The set $\J_1$ contains the following tuples: $(\alpha, \beta_2, h_2, v_3)$, $(\alpha, \beta_2, h_2, v_5)$, $(\alpha, \beta_2, h_5, v_3)$, and $(\alpha,$ $\beta_2, h_5, v_6)$. \qed

@@

\noindent {\underline{\em Example.} Let us examine, in turn, the two 2-tuples $\bm{t}_1 = (\alpha', \beta_1')$ and $\bm{t}_2 = (\alpha', \beta_2')$ in $\J(R_1', R_2')$. For $\bm{t}_1$, $B_{\bm{t}_1}$ is the rectangle \ttt{ABCD}, and $\gleft(\bm{t}_1) = \gbot(\bm{t}_1) = \alpha'$. Accordingly, $\dcross_H(\bm{t}_1) = \set{h_2}$ and $\dcross_V(\bm{t}_1) = \set{v_3}$. For $\bm{t}_2$, $B_{\bm{t}_2}$ is the rectangle \ttt{AEFG}, and $\gleft(\bm{t}_1) = \gbot(\bm{t}_1) = \alpha'$. Accordingly, $\dcross_H(\bm{t}_2) = \set{h_2, h_4, h_5}$ and $\dcross_V(\bm{t}_1) = \set{v_3, v_4, v_5}$.
\qed

\vspace{1mm}
\vgap

@@

\noindent {\underline{\em Example.} In our running example, the $\J^*$ computed includes 10 tuples in total: $(\alpha, \beta_1, h_2, v_3)$, and $\{\alpha\} \times \{\beta_2\} \times \set{h_2, h_4, h_5} \times \set{v_3, v_4, v_5}$. All these 10 tuples belong to $\J(R_1, R_2, H, V)$ and include the 4 tuples in $\J_1$ (mentioned earlier).
\qed
